Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-05-16 article-models-ttinternal.tex
starting to work on compatibility of weakening with itself

@@

@@

@@

An extension-weakening algebra in context $\Gamma$ will be an octuple
\begin{equation*}
(A,P,\epsilon_0,\epsilon_1,\phi_0,\phi_1,\omega_0,\omega_1)
\end{equation*}
where $(A,P,\epsilon_0,\epsilon_1,\phi_0,\phi_1)$ is an extension-empty algebra
in context $\Gamma$ and where
\begin{align*}
\jhom*
  {{{\Gamma}{A}}{P}}
  {\ctxwk{P}{P}}
  {\jcomp{}{\epsilon_0}{P}}
  {\omega_0}
  \\
\jfhom*
  {{{\Gamma}{A}}{P}}
  {\ctxwk{P}{P}}
  {\jcomp{}{\epsilon_0}{P}}
  {\omega_0}
  {\ctxwk{P}{\jcomp{}{\epsilon_0}{P}}}
  {\jcomp{}{\epsilon_0}{\jcomp{}{\epsilon_0}{P}}}
  {\omega_1}
\end{align*}
satisfying five(?) additional judgmental equalities expressing that $\omega_0$
and $\omega_1$ are compatible with $\epsilon_1$, $\phi_1$
and with each other. Our current goal is to figure out what these are.

@@

\subsubsection{The compatibility of weakening with itself}

>>>>

\begin{proof}
The proof follows from the fact that weakening by $A$ is compatible with all
the involved operations.
\end{proof}

@@

\begin{proof}
The proof follows from the fact that substitution with $x$ is compatible with
all the involved operations.
\end{proof}

@@

\begin{defn}
Let $(A,P,\phi_0,\phi_1)$ and $(B,Q,\psi_0,\psi_1)$ be empty algebras in context
$\Gamma$. An empty homomorphism from $(A,P,\phi_0,\phi_1)$ to $(B,Q,\psi_0,\psi_1)$
is a pair $(f_0,f_1)$ consisting of
\begin{align*}
\jhom*{\Gamma}{A}{B}{f_0}\\
\jfhom*{\Gamma}{A}{B}{f}{P}{Q}{f_1}
\end{align*}
satisfying the judgmental equalities
\begin{align*}
\jtermeq*{\Gamma}{B}{\subst{\phi_0}{f_0}}{\psi_0}\\
\jhomeq*{\Gamma}{A}{B}{\subst{\phi_0}{f_1}}{f_0}\\
\jtermeq*{{\Gamma}{A}}{\jcomp{}{f_0}{Q}}{\subst{\phi_1}{f_1}}{\jcomp{}{f_0}{\psi_1}}.
\end{align*}
\end{defn}

@@

An extension-weakening algebra in context $\Gamma$ will be an octuple
\begin{equation*}
(A,P,\epsilon_0,\epsilon_1,\phi_0,\phi_1,\omega_0,\omega_1)
\end{equation*}
where $(A,P,\epsilon_0,\epsilon_1,\phi_0,\phi_1)$ is an extension-empty algebra
in context $\Gamma$ and where
\begin{align*}
\jhom*
  {{{\Gamma}{A}}{P}}
  {\ctxwk{P}{P}}
  {\jcomp{}{\epsilon_0}{P}}
  {\omega_0}
  \\
\jfhom*
  {{{\Gamma}{A}}{P}}
  {\ctxwk{P}{P}}
  {\jcomp{}{\epsilon_0}{P}}
  {\omega_0}
  {\ctxwk{P}{\jcomp{}{\epsilon_0}{P}}}
  {\jcomp{}{\epsilon_0}{\jcomp{}{\epsilon_0}{P}}}
  {\omega_1}
\end{align*}
such that $(\omega_0,\omega_1)$ is both an extension homomorphism
\begin{equation*}
\begin{tikzcd}
( \ctxwk{P}{P},
  \ctxwk{P}{\jcomp{}{\epsilon_0}{P}},
  \ctxwk{P}{\epsilon_1},
  \ctxwk{P}{\jcomp{}{\epsilon_0}{\epsilon_1}})
\ar{r}{(\omega_0,\omega_1)}
& ( \jcomp{}{\epsilon_0}{P},
  \jcomp{}{\epsilon_0}{\jcomp{}{\epsilon_0}{P}},
  \jcomp{}{\epsilon_0}{\epsilon_1},
  \jcomp{}{\epsilon_0}{\jcomp{}{\epsilon_0}{\epsilon_1}})
\end{tikzcd}
\end{equation*}
and an empty homomorphism

satisfying five(?) additional judgmental equalities expressing that $\omega_0$
and $\omega_1$ are compatible with $\epsilon_1$, $\phi_1$
and with each other. Our current goal is to figure out what these are.

@@

\subsubsection{The compatibility of weakening with itself}
To express the compatibility of weakening with itself, we must fill in the
following diagram:
\begin{equation*}
\begin{tikzcd}
\ctxwk{P}{{P}{P}}
  \ar{r}{\ctxwk{P}{\omega_0}}
  \ar{d}[swap]{\ctxwk{{P}{P}}{\omega_0}}
& \ctxwk{P}{\jcomp{}{\epsilon_0}{P}}
  \ar{d}{\omega_1}
  \\
\ctxwk{{P}{P}}{\jcomp{}{\epsilon_0}{P}}
  \ar[densely dotted]{r}
& \jcomp{}{\omega_0}{\jcomp{}{\epsilon_0}{\jcomp{}{\epsilon_0}{P}}}
\end{tikzcd}
\end{equation*}
